---
title: "Small World Phenomenon in SCUT"
output:
  rmdformats::readthedown:
    self_contained: true
    lightbox: true
    gallery: false
    highlight: tango
    collapse: false
    smooth_scroll: true
    toc_depth: 3
    
author: 
  - name: 郭吉南
    affiliation: 201930031052@mail.scut.edu.cn
  - name: 何泽安
    affiliation: 202030020342@mail.scut.edu.cn
  - name: 张新镭
    affiliation: 202030101256@mail.scut.edu.cn
  - name: 杨赏纯
    affiliation: 202035020248@mail.scut.edu.cn
date: "2022-11-29"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Running Issues
1. This r markdown file provides codes to preprocess the raw dataset and model the social network graph problem. Several packages are required, **'readxl','xlsx','dplyr'**, which could be installed directly by running the commented codes in the chunk below, with the support of **Rtools**. 
```{r}
#install.packages('readxl')
#install.packages('xlsx')
#install.packages('dplyr')
```

2. The preprocessing process reads and operates on the raw dataset, **Six degree data.xls**, obtained from a large scale questionnaire in SCUT. **Data_preprocessed.xls** is the outcome of the Data preprocessing chunk.

3. The modeling process makes preparations for the use of package **igraph**, in the other r markdown file, **Data_analysis.rmd**. **Data_preprocessed.xls** is needed as input file. **Data_trimmed.csv** is the outcome of the modeling chunk and will be used as input file in the analysis process, in **Data_analysis.rmd**. ***One thing should be noted that the complete running time for the code in modeling process is 7~8 hours***, so you could run the analysis code with our provided trimmed dataset, **Data_trimmed.csv**.

4. All the r markdown and excel files, temporary and finally used could be found in **Small_World_Phenomenon_in_SCUT.zip**, also on github, [`Small World Phenomenon in SCUT`](https://github.com/GuanQinG-GitHub/Six-degree-separation-in-SCUT).

# Data preprocessing
```{r}
# library(readxl)
# library(xlsx)
# SDd <- read_excel("Six degree data.xls")
# 
# names(SDd)[names(SDd) == '1.您来自哪个学院？:校区'] <- 'your_campus'
# SDd$your_campus<-factor(SDd$your_campus,levels=c("国际校区","大学城校区","五山校区"),
#                           labels=c("GZIC","HEMC","WuShan")
#                  )
# 
# names(SDd)[names(SDd) == '1.您来自哪个学院？:二级标题'] <- 'your_acade'
# SDd$your_acade<-factor(SDd$your_acade,levels=c("吴贤铭智能工程学院","微电子学院","前沿软物质学院","未来技术学院","生物医学科学与工程学院","机械与汽车工程学院","建筑学院","土木与交通学院","电力学院","电子与信息学院","自动化科学与工程学院","材料科学与工程学院","化学与化工学院","食品科学与工程学院","轻工科学与工程学院","数学学院","物理与光电学院","工商管理学院","公共管理学院","马克思主义学院","外国语学院","计算机科学与工程学院","软件学院","环境与能源学院","生物科学与工程学院","经济与金融学院","旅游管理系","电子商务系","新闻传播学院","法学院","艺术学院","设计学院","医学院"),
#                           labels=c("A","B","C","D","E","F","G","H","I","J","K","L","M","N","O","P","Q","R","S","T","U","V","W","X","Y","Z","a","b","c","d","e","f","g")
#                  )
# 
# names(SDd)[names(SDd) == '3.您来自哪个年级？'] <- 'your_grade'
# SDd$your_grade<-factor(SDd$your_grade,levels=c("A.19级","B.20级","C.21级","D.22级","E.研究生"),
#                               labels=c("senior","junior","sophomore","freshman","graduate")
#                    )
# 
# names(SDd)[names(SDd) == '4.您是否参加过社团或学生组织？'] <- 'club_stud_org'
# SDd$club_stud_org<-factor(SDd$club_stud_org,levels=c("A.是","B.否"),
#                           labels=c("1","0")
#                  )
# 
# names(SDd)[names(SDd) == '5.您是否担任过班委？'] <- 'class_commi'
# SDd$class_commi<-factor(SDd$class_commi,levels=c("A.是","B.否"),
#                           labels=c("1","0")
#                  )
# 
# names(SDd)[names(SDd) == '6.您是否经常参加社交活动？'] <- 'soci_acti'
# SDd$soci_acti<-factor(SDd$soci_acti,levels=c("A.经常","B.不经常"),
#                           labels=c("1","0")
#                  )
# 
# names(SDd)[names(SDd) == '7.您课余生活是否丰富？'] <- 'dali_live'
# SDd$dali_live<-factor(SDd$dali_live,levels=c("A.丰富","B.不太丰富"),
#                           labels=c("1","0")
#                  )
# 
# names(SDd)[names(SDd) == '8.系唔系广东人?'] <- 'local'
# SDd$local<-factor(SDd$local,levels=c("A.系","B.唔系"),
#                           labels=c("1","0")
#                  )
# library(dplyr)
# DATA <- mutate(SDd,
#                    to_A = `2.您认识其他学院同学的大致人数？:吴贤铭智能工程学院-1~3` + `2.您认识其他学院同学的大致人数？:吴贤铭智能工程学院-4~10` + `2.您认识其他学院同学的大致人数？:吴贤铭智能工程学院->10`,
#                    to_B = `2.您认识其他学院同学的大致人数？:微电子学院-1~3` + `2.您认识其他学院同学的大致人数？:微电子学院-4~10` + `2.您认识其他学院同学的大致人数？:微电子学院->10`,
#                    to_C = `2.您认识其他学院同学的大致人数？:前沿软物质学院-1~3` + `2.您认识其他学院同学的大致人数？:前沿软物质学院-4~10` + `2.您认识其他学院同学的大致人数？:前沿软物质学院->10`,
#                    to_D = `2.您认识其他学院同学的大致人数？:未来技术学院-1~3` + `2.您认识其他学院同学的大致人数？:未来技术学院-4~10` + `2.您认识其他学院同学的大致人数？:未来技术学院->10`,
#                    to_E = `2.您认识其他学院同学的大致人数？:生物医学科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:生物医学科学与工程学院-4~10` +  `2.您认识其他学院同学的大致人数？:生物医学科学与工程学院->10`,
#                    to_F = `2.您认识其他学院同学的大致人数？:机械与汽车工程学院-1~3` + `2.您认识其他学院同学的大致人数？:机械与汽车工程学院-4~10` + `2.您认识其他学院同学的大致人数？:机械与汽车工程学院->10`,
#                    to_G = `2.您认识其他学院同学的大致人数？:建筑学院-1~3` + `2.您认识其他学院同学的大致人数？:建筑学院-4~10` + `2.您认识其他学院同学的大致人数？:建筑学院->10`,
#                    to_H = `2.您认识其他学院同学的大致人数？:土木与交通学院-1~3` + `2.您认识其他学院同学的大致人数？:土木与交通学院-4~10` + `2.您认识其他学院同学的大致人数？:土木与交通学院->10`,
#                    to_I = `2.您认识其他学院同学的大致人数？:电力学院-1~3` + `2.您认识其他学院同学的大致人数？:电力学院-4~10` + `2.您认识其他学院同学的大致人数？:电力学院->10`,
#                    to_J = `2.您认识其他学院同学的大致人数？:电子与信息学院-1~3` + `2.您认识其他学院同学的大致人数？:电子与信息学院-4~10` + `2.您认识其他学院同学的大致人数？:电子与信息学院->10`,
#                    to_K = `2.您认识其他学院同学的大致人数？:自动化科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:自动化科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:自动化科学与工程学院->10`,
#                    to_L = `2.您认识其他学院同学的大致人数？:材料科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:材料科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:材料科学与工程学院->10`,
#                    to_M = `2.您认识其他学院同学的大致人数？:化学与化工学院-1~3` + `2.您认识其他学院同学的大致人数？:化学与化工学院-4~10` + `2.您认识其他学院同学的大致人数？:化学与化工学院->10`,
#                    to_N = `2.您认识其他学院同学的大致人数？:食品科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:食品科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:食品科学与工程学院->10`,
#                    to_O = `2.您认识其他学院同学的大致人数？:轻工科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:轻工科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:轻工科学与工程学院->10`,
#                    to_P = `2.您认识其他学院同学的大致人数？:数学学院-1~3` + `2.您认识其他学院同学的大致人数？:数学学院-4~10` + `2.您认识其他学院同学的大致人数？:数学学院->10`,
#                    to_Q = `2.您认识其他学院同学的大致人数？:物理与光电学院-1~3` + `2.您认识其他学院同学的大致人数？:物理与光电学院-4~10` + `2.您认识其他学院同学的大致人数？:物理与光电学院->10`,
#                    to_R = `2.您认识其他学院同学的大致人数？:工商管理学院-1~3` + `2.您认识其他学院同学的大致人数？:工商管理学院-4~10` + `2.您认识其他学院同学的大致人数？:工商管理学院->10`,
#                    to_S = `2.您认识其他学院同学的大致人数？:公共管理学院-1~3` + `2.您认识其他学院同学的大致人数？:公共管理学院-4~10` + `2.您认识其他学院同学的大致人数？:公共管理学院->10`,
#                    to_T = `2.您认识其他学院同学的大致人数？:马克思主义学院-1~3` + `2.您认识其他学院同学的大致人数？:马克思主义学院-4~10` + `2.您认识其他学院同学的大致人数？:马克思主义学院->10`,
#                    to_U = `2.您认识其他学院同学的大致人数？:外国语学院-1~3` + `2.您认识其他学院同学的大致人数？:外国语学院-4~10` + `2.您认识其他学院同学的大致人数？:外国语学院->10`,
#                    to_V = `2.您认识其他学院同学的大致人数？:计算机科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:计算机科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:计算机科学与工程学院->10`,
#                    to_W = `2.您认识其他学院同学的大致人数？:软件学院-1~3` + `2.您认识其他学院同学的大致人数？:软件学院-4~10` + `2.您认识其他学院同学的大致人数？:软件学院->10`,
#                    to_X = `2.您认识其他学院同学的大致人数？:环境与能源学院-1~3` + `2.您认识其他学院同学的大致人数？:环境与能源学院-4~10` + `2.您认识其他学院同学的大致人数？:环境与能源学院->10`,
#                    to_Y = `2.您认识其他学院同学的大致人数？:生物科学与工程学院-1~3` + `2.您认识其他学院同学的大致人数？:生物科学与工程学院-4~10` + `2.您认识其他学院同学的大致人数？:生物科学与工程学院->10`,
#                    to_Z = `2.您认识其他学院同学的大致人数？:经济与金融学院-1~3` + `2.您认识其他学院同学的大致人数？:经济与金融学院-4~10` + `2.您认识其他学院同学的大致人数？:经济与金融学院->10`,
#                    to_a = `2.您认识其他学院同学的大致人数？:旅游管理系-1~3` + `2.您认识其他学院同学的大致人数？:旅游管理系-4~10` + `2.您认识其他学院同学的大致人数？:旅游管理系->10`,
#                    to_b = `2.您认识其他学院同学的大致人数？:电子商务系-1~3` + `2.您认识其他学院同学的大致人数？:电子商务系-4~10` + `2.您认识其他学院同学的大致人数？:电子商务系->10`,
#                    to_c = `2.您认识其他学院同学的大致人数？:新闻传播学院-1~3` + `2.您认识其他学院同学的大致人数？:新闻传播学院-4~10` + `2.您认识其他学院同学的大致人数？:新闻传播学院->10`,
#                    to_d = `2.您认识其他学院同学的大致人数？:法学院-1~3` + `2.您认识其他学院同学的大致人数？:法学院-4~10` + `2.您认识其他学院同学的大致人数？:法学院->10`,
#                    to_e = `2.您认识其他学院同学的大致人数？:艺术学院-1~3` + `2.您认识其他学院同学的大致人数？:艺术学院-4~10` + `2.您认识其他学院同学的大致人数？:艺术学院->10`,
#                    to_f = `2.您认识其他学院同学的大致人数？:设计学院-1~3` + `2.您认识其他学院同学的大致人数？:设计学院-4~10` + `2.您认识其他学院同学的大致人数？:设计学院->10`,
#                    to_g = `2.您认识其他学院同学的大致人数？:医学院-1~3` + `2.您认识其他学院同学的大致人数？:医学院-4~10` + `2.您认识其他学院同学的大致人数？:医学院->10`
#                    )
# 
# DATA <- SDd[,-c(3:110)]
# write.xlsx (DATA, file ="Data_preprocessed.xls")
```

# Data Modeling
```{r}
# library(readxl)
# DATA <- read_excel("Data_preprocessed.xls")
# 
# # Drop the first index column
# DATA = DATA[,2:length(names(DATA))]
# 
# # Create a function take letters out from a string
# letter_num_spilt = function(str){
#   str_splitted = strsplit(str,"")
#   letter_length = suppressWarnings(length(str_splitted[[1]][as.numeric(str_splitted[[1]][])>10]))
#   return(substr(str,1,letter_length))
# }
# 
# # Renumber interviewed students for graph establishing
# for (i in 1:length(DATA$your_acade)){
#   DATA$your_acade[i] = paste(letter_num_spilt(as.character(DATA$your_acade[i])),i,sep = "")
# }
# 
# # Take the information about links out
# DATA_links = DATA[1:length(DATA$your_acade), c(2,9:41)]
# 
# # Create a vector constitutes of all academies
# acade = c("A","B","C","D","E","F","G","H","I","J","K","L","M","N","O","P","Q","R","S","T","U","V","W","X","Y","Z","a","b","c","d","e","f","g")
# 
# # Create three vectors to store nodes and links
# nodes_from = c()
# nodes_end = c()
# dist_link = c()
# # create a vector to store all involved students
# student = c()
# 
# # Complete links in the academy-external network
# for (i in 1:length(DATA_links$your_acade)){
#   interviewee_i_neibs = DATA_links[i,2:length(DATA_links[1,])]
#   student = append(student,as.character(DATA_links[i,1]))
#   for (j in 1:length(interviewee_i_neibs)){
#     if (interviewee_i_neibs[j] != 0){
#       if (letter_num_spilt(as.character(DATA_links[i,1])) != acade[j]){
#         nodes_from = append(nodes_from,as.character(DATA_links[i,1]))
#         nodes_end = append(nodes_end,paste(acade[j],i,sep = ""))
#         dist_link = append(dist_link,as.double(interviewee_i_neibs[j]))
#         student = append(student,paste(acade[j],i,sep = ""))
#       }
#     }
#   }
# }
# 
# # Complete links in the academy-internal network
# for (i in 2:length(student)){
#   temp_acade = letter_num_spilt(student[i])
#   temp_student_list = student[1:i-1]
#   temp_student_neibs = temp_student_list[letter_num_spilt(temp_student_list) == temp_acade]
#   if (length(temp_student_neibs != 0)){
#       for (j in 1:length(temp_student_neibs)){
#       nodes_from = append(nodes_from,student[i])
#       nodes_end = append(nodes_end,temp_student_neibs[j])
#       dist_link = append(dist_link,1)
#   }
#   }
# }
# 
# # Store nodes and links into data frame
# nodes = data.frame(
#           id = student
# )
# links = data.frame(
#           from = nodes_from,
#           end = nodes_end,
#           dist = dist_link
# )
# 
# # Take out the distance-irrelevant attributes
# DATA_trimmed = DATA[,1:8]
# dist_sample = c()
# 
# # Compute the average social radius of each node
# for (i in 1:dim(DATA_trimmed)[1]){
#   # compute the shortest from the given node to all other nodes in the sample network
#   temp_dist = distances(net,v = V(net)[name == as.character(DATA_trimmed[i,2])], to = V(net))
#   # calculate the mean social radius of the given node
#   social_radius = mean(temp_dist)
#   dist_sample = append(dist_sample,social_radius)
# }
# 
# # Renumber interviewed students into more readable form
# for (i in 1:length(DATA_trimmed$your_acade)){
#   if (i > 1){
#     temp_acade = letter_num_spilt(as.character(DATA_trimmed$your_acade[i]))
#     temp_list = DATA_trimmed$your_acade[1:i-1]
#     acade_inter_neibs = temp_list[letter_num_spilt(as.character(temp_list)) == temp_acade]
#     temp_index = length(acade_inter_neibs) + 1
#     DATA_trimmed$your_acade[i] = paste(temp_acade,temp_index,sep = "")
#   }else{
#     DATA_trimmed$your_acade[1] = paste(letter_num_spilt(as.character(DATA_trimmed$your_acade[1])),1,sep = "")
#   }
# }
# 
# # Append a column containing average social radii of all interviewed students
# DATA_trimmed[,9] = dist_sample
# names(DATA_trimmed)[9] = "Social Radius"
# 
# # Export the final table after mathematical modeling
# write.table (DATA_trimmed, file ="DATA_trimmed.csv", sep =",", row.names =FALSE, col.names =TRUE, quote =TRUE)
```


